### 2021-04-19 architecture.tex
Qualify properties used in common precedence heuristics as "syntactic"

The symbol precedence heuristics commonly used in the \glspl{atp} sort the symbols by some numeric property
that is inexpensive to compute,
such as the number of occurrences in the input problem, or the symbol arity.
In our precedence recommender,
we sort the symbols by their costs $c$ produced by the \acrlong{nn} described in \cref{sec:gcn,sec:output}.
An advantage of this scheme is that sorting is a fast operation.

>>>>

The symbol precedence heuristics commonly used in the \glspl{atp} sort the symbols by some numeric syntactic property
that is inexpensive to compute,
such as the number of occurrences in the input problem, or the symbol arity.
In our precedence recommender,
we sort the symbols by their costs $c$ produced by the \acrlong{nn} described in \cref{sec:gcn,sec:output}.
An advantage of this scheme is that sorting is a fast operation.
